Spatial variation in allometric growth of invasive lionfish has management implications

### 2019-02-05 docs/Manuscript.tex
Added changes by Sean

\begin{abstract}
Lionfish (\textit{Pterois volitans / miles}) are an invasive species in
the Western Atlantic and the Caribbean. Improving management of invasive
lionfish populations requires accurate total biomass estimates, which
depend on accurate estimates of allometric growth. Sedentary species
like lionfish often exhibit high levels of spatial variation in life
history characteristics. We review 17 published length-weight
relationships for lionfish taken throughout their invasive range and
found regional differences that led to significant under- and
overestimation of weight estimates. The spatial pattern we observed is
consistent with findings from other studies focusing on genetics or
length-at-age. We show that the use of \textit{ex situ} parameters can
result in up to a threefold under- or overestimation of total weight,
but using parameters from nearby regions reduces this error. These
findings can have substantial implications for management in terms of
predicting effects on local ecosystems, evaluating the effectiveness of
removal programs, or estimating biomass available for harvest.
\end{abstract}

@@

A substantial amount of research describes lionfish impacts throughout
its invaded range. A meta-analysis by \citet{peake_2018} showed that
invasive lionfish prey on at least 167 different species across the
tropical and temperate Western Atlantic. Their feeding behavior and high
consumption rates can reduce recruitment and population sizes of native
reef-fish species, and can further endanger reef fish
\citep{green_2012,rocha_2015}; but see \citet{hackerott_2017}. For
example, field experiments by \citet{albins_2008} showed that lionfish
establishment led to reduced recruitment of native fishes by nearly 80\%
over a five-week period in the Bahamas. \citet{green_2012} reported that
prey fish biomass declined by 65\% over two years as lionfish biomass
increased along Bahamian coral reefs. However, their trophic impacts can
be minimized if local lionfish biomass is controlled by culling
\citep{ariasgonzalez_2011}.

Governments and non-profit organizations have sought to reduce lionfish
densities through removal programs and incentivizing its consumption
\citep{chin_2016}. In some cases, these have shown to significantly
reduce --but not quite eliminate-- lionfish abundances at local scales
\citep{deleon_2013,sandel_2015}. Complete eradication of lionfish
through fishing is unlikely because of their rapid recovery rates and
ongoing recruitment to shallow-water areas from persistent populations
in mesophotic ecosystems \citep{barbour_2011,andradibrown_2017}.
However, promoting lionfish consumption might create a level of demand
capable of incentivizing a stable fishery while controlling
shallow-water populations, thus creating alternative livelihoods and
avoiding further negative effects to local biota.

@@

Outcomes of previous studies suggest lionfish are likely to exhibit
spatial heterogeneity in the length-weight relationship, which we
summarize in two main causes. First, culling programs are effective in
reducing local adult populations largely because lionfish exhibit high
levels of site fidelity and small home ranges
\citep{Fishelson_1997,kochzius_2005,jud_2012,cote_2014}. It is known
that fish with sedentary behavior are likely to exhibit high levels of
spatial variation in important life history characteristics such as
growth or natural mortality rates
\citep{gunderson_2008,hutchinson_2008,wilson_2012,guan_2013}. Second,
genetic analysis of lionfish suggests biological differences due to the
existence of two genetically distinct invasive subpopulations between
the Western Atlantic and the Caribbean \citep{betancurr_2011}. The large
number of site-specific studies reporting the length-weight relationship
of lionfish provide variable estimates. These differences may be
increasingly important when estimating the potential effectiveness of
lionfish culling programs
\citep{barbour_2011,morris_2011,cote_2014,johnston_2015}. However, the
magnitude of the error caused by using \emph{ex situ} parameters to
estimate total weight from length observations remains unexplored.

Here, we use previously published length-weight relationships for
lionfish populations in North Carolina, Northern and Southern Gulf of
Mexico, the Southern Mexican Caribbean, Bahamas, Little Cayman, Jamaica,
Bonaire, Puerto Rico, and Costa Rica to quantify the magnitude of the
error caused by using \emph{ex situ} parameters to estimate lionfish
weight from length observations. We also collected lionfish length and
weight data in the central Mexican Caribbean and report the first
length-weight relationship for this region.

@@

We reviewed 12 published studies and obtained 17 length-weight
relationships for the Western Atlantic (n = 2), Gulf of Mexico (n = 7),
and Caribbean (n = 8, Table \ref{tab:all_params}, Fig \ref{fig:map}). We
collected information on sex differentiation, location, length and depth
ranges and sampling methods from each study when available. Only two
studies reported parameters for each gender
\citep{aguilarperera_2016,fogg_2013}, so we assumed both genders were
included in a study if gender was unspecified. Reviewed studies
presented information for organisms ranging between 25 mm and 475 mm in
Total Length (\(TL\)), and that were obtained at depths between 0.5 m
and 57 m. Four studies explicitly stated that their organisms were
sampled with pole spears
\citep{dahl_2014,aguilarperera_2016,chin_2016,sabidoitz_2016}, and six
studies mentioned that some of their organisms were obtained with pole
spears (or other type of harpoon) but also hand-held nets or fish traps
\citep{barbour_2011,fogg_2013,edwards_2014,toledohernndez_2014,sandel_2015,sabidoitza_2016},
and two studies did not specify how organisms were sampled
\citep{darling_2011,deleon_2013}.

@@

We also used data from \citet{villaseorderbez_2014}, who collected
organisms from 10 sampling sites along the central Mexican Caribbean
coast in the Summer of 2010 (Supplementary Table 1). Sampling locations
included wall and carpet reefs at depths between 5.7 m and 38.1 m. All
observed lionfish (n = 109) were collected using hand nets and numbered
collection bottles. The use of hand nets prevented any weight loss due
to bleeding and allowed better representation of small sizes by avoiding
gear selectivity. Organisms were euthanized via pithing and Total Length
(TL; mm) and Total Weight (TW; g) were recorded.

The weight-at-length relationship for lionfish in the central Mexican
Caribbean was calculated with the allometric growth function:

@@

Where \(a\) is the ponderal index and \(b\) is the scaling exponent or
allometric parameter.

The above equation was linearized using \(log_{10}\)-transformation. The
coefficients were estimated with an Ordinary Least Squares Regression,
and heteroskedastic-robust standard error correction was applied
\citep{zeileis_2004}. When \(b = 3\), it is said that the organism
exhibits a perfect isometric growth, so the \(b\) coefficient was tested
against the null hypothesis of isometric growth (\emph{i.e.}
\(H_0: b = 3\)). Coefficients were tested with a two-tailed Student's t,
and the significance of the regression was corroborated with an F-test.

@@

We obtained a total of 18 parameter pairs by combining length-weight
parameters extracted from the literature and the additional pair
calculated here. Recall that the objective of this study is not to
describe variations between populations, but rather to estimate how the
use of \emph{ex situ} parameters influences weight estimates. We used
the central Mexican Caribbean as a case study of how the use of \emph{ex
situ} parameters influences the accuracy of weight estimates for
lionfish. We estimated \(TW\) from the \(TL\) observations we collected
in the central Mexican Caribbean (n = 109, with \(TL\) ranging from 34
mm to 310 mm) using each of the 18 parameter pairs and divided predicted
weights by known observed weights to obtain a simple measure of over- or
underestimation. Difference in mean weight ratios were tested with an
analysis of covariance (ANCOVA), where the sources of variation were the
study and \(TL\). Ratios were logit-transformed prior to analysis, and a
\emph{post-hoc} Tukey's test was used to identify groups where mean
ratios did not differ. All analyses were performed in R version 3.5.2
\citep{rcore_2018}. Raw data and code used in this work are available on
github at github.com/jcvdav/lionfish\_biometry.

@@

The length-weight relationship for organisms from the central Mexican
Caribbean resulted in coefficient values of
\(a = 3.2056297\times 10^{-6}\) and \(b = 3.2347391\) (\(R^2 = 0.977\),
F(df = 1; 107) = 6928.67, \(p < 0.001\)). The allometric factor (\(b\))
was significantly different from \(b = 3\) (\(t(107) = 6.04; p<0.001\))
corroborating that lionfish present allometric growth. The length-weight
coefficients estimated in this study were within the range identified by
studies in other regions (Table \ref{tab:all_params}). Figure
\ref{fig:l-w-carib} shows the relationship between TL and TW for this
region.

@@

There were significant differences in our predicted weights for the
central Mexican Caribbean when using each of the different pairs of
parameters (\(F(df = 17; 1943) = 24.96; p < 0.001\)). The lowest weight
estimates for the observed lengths resulted from using the allometric
parameters from Banco Chinchorro in the Caribbean, with mean \(\pm\) SD
of 40.37 \(\pm\) 58.74 g \citep{sabidoitz_2016}. In contrast, the
highest weight estimates came from the Western Atlantic with 73.76
\(\pm\) 96.11 g \citep{barbour_2011}. To put this in context, true
observed weights have a mean of 52.56 \(\pm\) 76.58 g. Weights predicted
from these extreme parameters correspond to mean \(\pm\) SD
predicted-to-observed weights ratios of 0.80 \(\pm\) 0.19 and 1.76
\(\pm\) 0.50 (mean \(\pm\) SD), respectively. The largest under- and
overestimations resulted in ratios of 0.36 and 3.51 of the actual
observed weight, indicating that \emph{ex situ} parameters can result in
substantial weight under- and overestimation.

Tukey's \emph{post-hoc} test suggests that weight ratios for the central
Mexican Caribbean were not different from those obtained with parameters
from Little Cayman, the Bahamas, and some sites in the Gulf of Mexico
(Tukey's HSD \(p > 0.05\)). Weight estimates using parameters from the
Gulf of Mexico and Western Atlantic were higher on average than those
from the Caribbean (Fig \ref{fig:all_allo}). The average (\(\pm\) SD)
predicted-to-observed weight ratios from these three regions were 1.24
\(\pm\) 0.309, 1.76 \(\pm\) 0.496, and 1.17 \(\pm\) 0.398, respectively.
This suggest that the smallest errors are observed when using parameters
other locations in the Caribbean. Predicted-to-observed weight ratios
are presented in Figure \ref{fig:bio_ratio}.

\caption{\label{tab:unnamed-chunk-7}\label{tab:all_params}Summary of 18 allometric growth parameters available for lionfish in the invaded range from peer-reviewed literature and this study. All parameters have been adjusted to convert from millimeters to grams. n = Sample size, Sex specifies whether data was presented for Females (F), Males (M), or both genders combined (B), a = scaling parameter (presented in $\times 10^{-5}$), b = exponent.}
\centering
\begin{tabular}{llllrll}
\toprule
Region & Sex & n & a & b & $R^2$ & Reference\\
\midrule
Western Atlantic & B & 774 & 2.9 & 2.89 & - & Barbour et al., 2011\\
Western Atlantic & B & - & 0.25 & 3.29 & - & Darling et al., 2011\\
GoM & B & 934 & 0.21 & 3.34 & 0.98 & Dahl \& Patterson, 2014\\
GoM & B & 472 & 0.29 & 3.30 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
GoM & F & 67 & 0.12 & 3.47 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
\addlinespace
GoM & M & 59 & 0.42 & 3.23 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
GoM & B & 582 & 0.14 & 3.43 & 0.99 & Fogg et al., 2013\\
GoM & M & 119 & 0.27 & 3.31 & 0.97 & Fogg et al., 2013\\
GoM & F & 115 & 0.68 & 3.14 & 0.94 & Fogg et al., 2013\\
Caribbean & B & 458 & 3.6 & 2.81 & - & Sandel et al., 2015\\
\addlinespace
Caribbean & B & 419 & 2.8 & 2.85 & 0.87 & Chin et al., 2016\\
Caribbean & B & 1450 & 2.3 & 2.89 & 0.92 & de Leon et al., 2013\\
Caribbean & B & 1887 & 0.3 & 3.24 & 0.97 & Edwards et al., 2014\\
Caribbean & B & 2143 & 0.52 & 3.18 & 0.99 & Sabido-Itza et al., 2016\\
Caribbean & B & 227 & 0.8 & 3.11 & 0.96 & Toledo-Hernández et al., 2014\\
\addlinespace
Caribbean & B & 449 & 0.23 & 3.25 & 0.97 & Sabido-Itza et al., 2016b\\
Caribbean & B & 368 & 0.32 & 3.19 & 0.98 & Sabido-Itza et al., 2016b\\
Caribbean & B & 109 & 0.32 & 3.23 & 0.98 & This study\\
\bottomrule
\end{tabular}
\end{table}

\begin{figure}
\centering
\includegraphics{Manuscript_files/figure-latex/fit2-1.pdf}
\caption{\label{fig:all_allo}Length-weight relationships (n = 18) for 12
studies and this study. The curves are shown for the range of lengths
reported in each study (See Supplementary Table 2); when ranges were not
present, we use the ones found in this study (34 mm - 310 mm). Colors
indicate studies from which the parameters were extracted. Dotted,
dashed, and solid lines show models for males, females, and combined
sexes, respectively. The dashed black line represents the relationship
estimated in this study. There are two solid green lines for Sabido-Itza
et al, 2016b, one for each of the two sites for which they report
parameters. A log-log version of this figure is presented in Figure S4.}
\end{figure}

@@

Our results suggest that lionfish exhibit highly variable allometric
relationships across the invaded range, and that this variation is
spatially heterogeneous and relevant for management of the invasion.
Moreover, we show that the use of \emph{ex situ} parameters may lead to
highly biased weight estimates. Our comparison of observed weights to
those predicted with locally-informed parameters and \emph{ex situ}
parameters showed that weight can be overestimated by more than a
three-fold, and highlights the need to use local information. Here we
discuss the implications of our findings, possible shortcommings in our
analyses, and highlight potential future research directions.

@@

We might be inclined to attribute all variation to the spatial origin of
these parameters. However, these were not only collected for different
locations, but also using a range of different sampling methods and at
different points in time (See Supplementary Table 2 for an extended
version of Table 1). While we are not able to evaluate how these factors
influence previous estimates (raw data from all studies would be
needed), it is certain that the lack of locally-calculated parameters
may induce significant bias when calculating weight from length
observations. Differences in weight-at-length could also reflect
differential energy input or usage, or a combination of both. The
magnitude of the bias and our lack of understanding of the source of
variation highlights the need to simultaneously collect length-weight
information across the invaded range to test for spatially-induced
patterns and link these to previously suggested environmental and
genetic structures. Such an endeavor would provide insights into
lionfish biology and better inform management.

Applying parameters estimates to lengths outside the range of lengths
originally used to estimate the parameters may also induce error. Our
smallest observed organism was 34 mm in \(TL\), and only two studies
estimated parametrs with smaller organisms
\citep{sabidoitza_2016,edwards_2014}. On the other hand, our largest
organism had a \(TL\) of 310 mm, which is well within the range of all
other studies (maximum observed lengths varied from 325 mm to 475 mm;
See Supplementary Table 2). Due to the power-function describing the
allometric relationship, the error is higher when extrapolation is done
for lengths that are larger than the maximum length used to estimate the
parameters. This means that not only must managers use locally-informed
data, but that these local data must also include the full range of
lengths present in the region to reduce error caused by extrapolation.

The results presented here have fundamental implications for management.
For example, \citet{edwards_2014} simulated a lionfish culling program
under two scenarios, one using length-at-age and length-to-weight
parameters from North Carolina and one using parameters from Little
Cayman. Their results show that using different parameters caused up to
a four-year difference in the time required for the simulated lionfish
population to recover to 90\% of its initial biomass after removals
ceased. Here, we show that using one set of length-weight parameters
versus another for a given length can result in more than a threefold
under- or overestimation of total weight. These differences become
especially important when allocating resources for lionfish removal
programs, incentivizing lionfish fisheries as a source of alternative
livelihoods, or estimating ecosystem impacts. Research efforts focused
on invasive lionfish populations need to use parameters calculated for
their region to the extent possible, or at least use reasonable sets of
different parameters that provide upper and lower bounds in their
results.

>>>>

\begin{abstract}
Lionfish (\textit{Pterois volitans / miles}) are an invasive species in
the Western Atlantic and the Caribbean. Improving management of invasive
lionfish populations requires accurate total biomass estimates, which
depend on accurate estimates of allometric growth, but sedentary species
like lionfish often exhibit high levels of spatial variation in life
history characteristics. We reviewed 17 published length-weight
relationships for lionfish taken throughout their invasive range and
found regional differences that led to significant under- and
overestimation of weight estimates. The spatial pattern we observed is
consistent with findings from other studies focused on genetics or
length-at-age. We show that the use of \textit{ex situ} parameters can
result in up to a threefold under- or overestimation of total weight,
but using parameters from nearby regions substantially reduces this
error. These findings can have implications for management in terms of
predicting effects on local ecosystems, evaluating the effectiveness of
removal programs, or estimating biomass available for harvest.
\end{abstract}

@@

A substantial amount of research describes lionfish impacts throughout
its invaded range. A meta-analysis by \citet{peake_2018} showed that
invasive lionfish prey on at least 167 different species across the
tropical and temperate Western Atlantic. Their feeding behavior and high
consumption rates can reduce recruitment and population sizes of native
reef-fish species, and can further endanger reef fish
\citep[][but see \citealt{hackerott_2017} for a counterexample]{green_2012,rocha_2015}.
For example, field experiments showed that lionfish establishment in the
Bahamas led to reduced recruitment of native fishes by nearly 80\% over
a five-week period \citep{albins_2008}, and prey fish biomass declined
by 65\% over two years as lionfish biomass increased along Bahamian
coral reefs \citep{green_2012}. However, trophic impacts of lionfish can
be minimized if their local biomass is controlled by culling
\citep{ariasgonzalez_2011}.

Governments and non-profit organizations have sought to reduce lionfish
densities through removal programs and incentivizing its consumption
\citep{chin_2016}. In some cases, these have shown to significantly
reduce -- but not quite eliminate -- lionfish abundances at local scales
\citep{deleon_2013,sandel_2015}. Complete eradication of lionfish
through fishing is unlikely because of their rapid recovery rates and
ongoing recruitment to shallow-water areas from persistent populations
in mesophotic ecosystems \citep{barbour_2011,andradibrown_2017}.
However, promoting lionfish consumption might create a level of demand
capable of incentivizing a stable fishery while controlling
shallow-water populations, thus creating alternative livelihoods and
avoiding further negative effects to local biota.

@@

Outcomes of previous studies suggest lionfish are likely to exhibit
spatial heterogeneity in the length-weight relationship for two main
reasons. First, fish with sedentary behavior such as lionfish often
exhibit high levels of spatial variation in important life history
characteristics such as growth or natural mortality rates
\citep{gunderson_2008,hutchinson_2008,wilson_2012,guan_2013}. In fact,
culling programs are effective in reducing local adult populations
largely because lionfish have high levels of site fidelity and small
home ranges \citep{Fishelson_1997,kochzius_2005,jud_2012,cote_2014}.
Second, genetic analysis of lionfish suggests biological differences due
to the existence of two genetically distinct invasive subpopulations
between the Western Atlantic and the Caribbean \citep{betancurr_2011}.
Site-specific studies that calculate the length-weight relationship of
lionfish report variable estimates, and these differences may be
increasingly important when estimating the potential effectiveness of
lionfish culling programs
\citep{barbour_2011,morris_2011,cote_2014,johnston_2015}. However, the
influence of using \emph{ex situ} parameters when estimating the
length-weight relationship remains unexplored.

Our objective was to quantify the magnitude of error caused by using
\emph{ex situ} parameter values when estimating lionfish weight from
length observations. In this study, we calculated and reported the first
length-weight relationship for lionfish in the central Mexican Caribbean
(n = 109). We then estimated lionfish weight in this area using
previously published length-weight relationships for lionfish
populations in North Carolina, the Northern and Southern Gulf of Mexico,
the Southern Mexican Caribbean, the Bahamas, Little Cayman, Jamaica,
Bonaire, Puerto Rico, and Costa Rica. By comparing these weight
estimates to the \emph{in situ} length-weight observations, we showed
that using \emph{ex situ} parameter values resulted in up to a threefold
under- or overestimation of lionfish weight.

We reviewed 12 published studies and obtained 17 length-weight
relationships for the Western Atlantic (n = 2), Gulf of Mexico (n = 7),
and Caribbean (n = 8, Table \ref{tab:all_params}, Fig \ref{fig:map}). We
collected information on sex differentiation, location, length and depth
ranges, and sampling methods from each study when available. Only two
studies reported parameters for each sex
\citep{aguilarperera_2016,fogg_2013}, so we assumed data from both sexes
were combined in a study if sex was unspecified. Reviewed studies
presented information for organisms ranging from 25-475 mm in Total
Length (\(TL\)) and were obtained at depths between 0.5 m and 57 m. Four
studies explicitly stated that their organisms were sampled with pole
spears \citep{dahl_2014,aguilarperera_2016,chin_2016,sabidoitz_2016},
and six studies mentioned that some of their organisms were obtained
with pole spears (or other type of harpoon) but also hand-held nets or
fish traps
\citep{barbour_2011,fogg_2013,edwards_2014,toledohernndez_2014,sandel_2015,sabidoitza_2016}.
Two studies did not specify how organisms were sampled
\citep{darling_2011,deleon_2013}.

We also used data from 109 lionfish sampled by
\citet{villaseorderbez_2014}, who used hand nets and numbered bottles to
collect organisms from 10 sampling sites along the central Mexican
Caribbean coast in the Summer of 2010 (Supplementary Table 1). Sampling
locations included wall and carpet reefs at depths between 5.7 m and
38.1 m. The use of hand nets prevented any weight loss due to bleeding
and allowed better representation of small sizes by avoiding gear
selectivity. Organisms were euthanized via pithing and Total Length (TL;
mm) and Total Weight (TW; g) were recorded.

@@

@@

The weight-at-length relationship for lionfish in the central Mexican
Caribbean was calculated with the allometric growth function

@@

where \(a\) is the ponderal index and \(b\) is the scaling exponent or
allometric parameter. We linearized the equation using
\(log_{10}\)-transformation and estimated the coefficients using an
Ordinary Least Squares Regression with a heteroskedastic-robust standard
error correction \citep{zeileis_2004}. Coefficients were tested with a
two-tailed Student's t-test, and the significance of the regression was
corroborated with an F-test.

@@

We obtained a total of 18 parameter pairs by combining length-weight
parameters extracted from the literature and the additional pair
calculated here. Recall that the objective of this study is not to
describe variations between populations, but rather to estimate how the
use of \emph{ex situ} parameters influences the accuracy of weight
estimates for lionfish, using the central Mexican Caribbean as a case
study. Using each of the 18 parameter pairs, we estimated \(TW\) from
the \(TL\) observations collected in the central Mexican Caribbean (n =
109, with \(TL\) ranging from 34 mm to 310 mm) and divided predicted
weights by known observed weights to obtain a simple measure of over- or
underestimation. Difference in mean weight ratios were tested with an
analysis of covariance (ANCOVA), where the sources of variation were the
study and \(TL\). Ratios were logit-transformed prior to analysis, and a
\emph{post-hoc} Tukey's test was used to identify groups where mean
ratios did not differ. All analyses were performed in R version 3.5.2
\citep{rcore_2018}. Raw data and code used in this work are available on
github at github.com/jcvdav/lionfish\_biometry.

\caption{\label{tab:unnamed-chunk-2}\label{tab:all_params}Summary of 18 allometric growth parameters available for lionfish in the invaded range from peer-reviewed literature and this study. All parameters have been adjusted to convert from millimeters to grams. n = Sample size, Sex specifies whether data was presented for Females (F), Males (M), or both sexes combined (B), a = scaling parameter (presented in $\times 10^{-5}$), b = exponent.}
\centering
\begin{tabular}{llllrll}
\toprule
Region & Sex & n & a & b & $R^2$ & Reference\\
\midrule
Western Atlantic & B & 774 & 2.90 & 2.89 & - & Barbour et al., 2011\\
Western Atlantic & B & - & 0.25 & 3.29 & - & Darling et al., 2011\\
GoM & B & 934 & 0.21 & 3.34 & 0.98 & Dahl \& Patterson, 2014\\
GoM & B & 472 & 0.29 & 3.30 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
GoM & F & 67 & 0.12 & 3.47 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
\addlinespace
GoM & M & 59 & 0.42 & 3.23 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
GoM & B & 582 & 0.14 & 3.43 & 0.99 & Fogg et al., 2013\\
GoM & M & 119 & 0.27 & 3.31 & 0.97 & Fogg et al., 2013\\
GoM & F & 115 & 0.68 & 3.14 & 0.94 & Fogg et al., 2013\\
Caribbean & B & 458 & 3.60 & 2.81 & - & Sandel et al., 2015\\
\addlinespace
Caribbean & B & 419 & 2.80 & 2.85 & 0.87 & Chin et al., 2016\\
Caribbean & B & 1450 & 2.30 & 2.89 & 0.92 & de Leon et al., 2013\\
Caribbean & B & 1887 & 0.30 & 3.24 & 0.97 & Edwards et al., 2014\\
Caribbean & B & 2143 & 0.52 & 3.18 & 0.99 & Sabido-Itza et al., 2016\\
Caribbean & B & 227 & 0.80 & 3.11 & 0.96 & Toledo-Hernández et al., 2014\\
\addlinespace
Caribbean & B & 449 & 0.23 & 3.25 & 0.97 & Sabido-Itza et al., 2016b\\
Caribbean & B & 368 & 0.32 & 3.19 & 0.98 & Sabido-Itza et al., 2016b\\
Caribbean & B & 109 & 0.32 & 3.23 & 0.98 & This study\\
\bottomrule
\end{tabular}
\end{table}

@@

The length-weight relationship for organisms from the central Mexican
Caribbean resulted in coefficient values of \(a = 3.206e-06\) and
\(b = 3.235\) (\(R^2 = 0.977\), \(F_{1, 107} = 6928.67; p < 0.001\)).
The allometric factor (\(b\)) was significantly different from \(b = 3\)
(\(t_{107} = 6.04; p<0.001\)) corroborating that lionfish present
allometric growth. The length-weight coefficients estimated here were
within the range identified by studies from other regions (Table
\ref{tab:all_params}). Figure \ref{fig:l-w-carib} shows the relationship
between TL and TW for this region.

@@

There were significant differences in our predicted weights for the
central Mexican Caribbean when using each of the different pairs of
parameters (\(F_{17, 1943} = 24.96; p < 0.001\)). The lowest weight
estimates for the observed lengths resulted from using the allometric
parameters from Banco Chinchorro in the Caribbean, with mean \(\pm\) SD
of 40.37 \(\pm\) 58.74 g \citep{sabidoitz_2016}. In contrast, the
highest weight estimates came from the Western Atlantic with 73.76
\(\pm\) 96.11 g \citep{barbour_2011}. To put this in context, true
observed weights have a mean of 52.56 \(\pm\) 76.58 g. Weights predicted
from these extreme parameters correspond to predicted-to-observed weight
ratios of 0.80 \(\pm\) 0.19 and 1.76 \(\pm\) 0.50 (mean \(\pm\) SD),
respectively. The largest under- and overestimations resulted in ratios
of 0.36 and 3.51 of the actual observed weight, indicating that \emph{ex
situ} parameters can result in highly erroneous weight estimates.

Tukey's \emph{post-hoc} test suggests that weight ratios for the central
Mexican Caribbean were not different from those obtained with parameters
from Little Cayman, the Bahamas, and some sites in the Gulf of Mexico
(Tukey's HSD \(p > 0.05\)). All weight estimates using parameters from
the Gulf of Mexico and Western Atlantic were higher than observed
values, and only parameters from the Caribbean produced weights smaller
than observed (Fig \ref{fig:bio_ratio}). The regional average (\(\pm\)
SD) of predicted-to-observed weight ratios from these three regions were
1.24 \(\pm\) 0.309, 1.41 \(\pm\) 0.523, and 1.20 \(\pm\) 0.423 for the
Gulf of Mexico, Western Atlantic, and Caribbean, respectively. This
suggests that the smallest errors are observed when using parameters
from other locations in the Caribbean. Predicted-to-observed weight
ratios are presented in Figure \ref{fig:bio_ratio}.

\begin{figure}
\centering
\includegraphics{Manuscript_files/figure-latex/fit2-1.pdf}
\caption{\label{fig:all_allo}Length-weight relationships (n = 18) for 12
studies and this study. The curves are shown for the range of lengths
reported in each study (See Supplementary Table 2); when ranges were not
present, we use the ones found in this study (34 mm - 310 mm). Colors
indicate studies from which the parameters were extracted. Dotted,
dashed, and solid lines show models for males, females, and combined
sexes, respectively. Letters in parentheses indicate if the study comes
from the Gulf of Mexico (GoM), Western Atlantic (WA), or Caribbean (Ca).
The dashed black line represents the relationship estimated in this
study. There are two solid green lines for Sabido-Itza et al, 2016b, one
for each of the two sites for which they report parameters. A log-log
version of this figure is presented in Figure S4.}
\end{figure}

@@

Our results suggest that lionfish exhibit highly variable, spatially
heterogeneous allometric relationships across their invaded range, and
that this variation is relevant for managing invasions. Moreover, we
show that the use of \emph{ex situ} parameter values may lead to highly
biased weight estimates. Our comparison of observed weights to those
predicted with locally-informed parameters and \emph{ex situ} parameters
showed that weight can be overestimated by more than threefold,
highlighting the need to use local information. Here we discuss the
implications of our findings, possible shortcommings in our analyses,
and highlight potential future research directions.

@@

We might be inclined to attribute all variation in the lionfish
length-weight relationship to the spatial origin of these parameters.
However, samples from the 12 studies included here were not only
collected in different locations, but also at different points in time
and across different depth and size ranges (See Supplementary Table 2
for an extended version of Table 1 that incorporates these variables
when available). While we could not evaluate how these factors influence
previous estimates without the necessary raw data from every study, we
still show that the lack of locally-calculated parameters can induce
significant bias when calculating weight from length observations. The
magnitude of the bias discovered in this study and our lack of
understanding the sources driving spatial variation for lionfish
highlights the need to simultaneously collect length-weight information
across the invaded range to test for spatially-induced patterns and to
link these findings to previously suggested environmental and genetic
structures. Such an endeavor would provide insight into lionfish biology
and better inform management.

Applying parameters estimates to lengths outside the range of lengths
originally used to estimate the parameters may also induce error. Our
smallest observed organism was 34 mm in \(TL\), and only two studies
estimated parametrs with smaller organisms
\citep{edwards_2014,sabidoitza_2016}. However, our largest organism had
a \(TL\) of 310 mm, which is well within the range of all other studies
(the next smallest maximum length was 325 mm; See Supplementary Table
2). Due to the power function describing the allometric relationship
(\emph{i.e.} Eq. 1), the error is larger when extrapolation is done for
lengths that are larger than the maximum length used to estimate the
parameters.

The results presented here have key implications for management. For
example, \citet{edwards_2014} simulated a lionfish culling program under
two scenarios, one using length-at-age and length-to-weight parameters
from North Carolina and one using parameters from Little Cayman. Their
results show that using different parameters caused up to a four-year
difference in the time required for the simulated lionfish population to
recover to 90\% of its initial biomass after removals ceased. Here, we
show that using one set of length-weight parameters versus another for a
given length can result in more than a threefold under- or
overestimation of total weight. These differences become especially
important when allocating resources for lionfish removal programs,
incentivizing lionfish fisheries as a source of alternative livelihoods,
or estimating ecosystem impacts. Research efforts focused on invasive
lionfish populations need to use parameters calculated for their region
to the extent possible, or use different sets of parameters that provide
appropriate upper and lower bounds in their results.
